---
title: "ChinaCheers"
author: "wenlarry"
date: "2/17/2017"
output: html_document
---
#Preamble

China's internal debt increased exponentially from about US$2.0T in 2010 to 
US$3.5T in 2016, while GDP during this period grew only by 
US$750Bn and US$1200Bn respectively. Such a massive debt induced growth over the past 2 decades is not impressive, and the trend continues. 

Chart 1 (A basic Bubble Chart) displays this critical flaw in China's economy.

Another weak indicator is the demography. The core population i.e. (25/54 yr/old population) has peaked at 675 m in 2016. This core population is the crucible of China's production and consumption growth in the decades ahead. Economic growth through domestic consumption will be a challenge.

Chart 2 (A 3D Scatter Plot) displays all the 3 adverse indicators interactively. (Also, this augments the point that where 2 or more critical dependent variables are to be presented in 1 chart, the 3D chart is preferred over the mundane X/Y axis chart). 

Regarding the demographic challenge and the debt overhang on China's growth, are these 'China Cheers' or 'China Tears' going forward ?


Note: The 2 charts are constructed from 'plotly'.

Citation: China's data are in Chris Hamilton's Econimica blog, published for the public on Feb 15, 2017.


#Chart 1 (Debt fueling GDP growth) 


##A basic Bubble Chart.


```{r,echo=FALSE}
suppressMessages(library(plotly))
p<-plot_ly(
x=c(250,400,2000,3500),
y=c(200,250,750,1200),
 type='scatter',mode= 'markers',   size=c(60,70,80,90), 
 marker=list(color="violet"))%>% 
 add_markers()%>% 
 layout(title= 'China-Changes in Debt & GDP (1990 - 2006)',
        xaxis=list(title = 'Debt US$ Bn'),
        yaxis=list(title = 'GDP US$ Bn'))
p
 
```

#Chart 2 (Headwinds of Debt and Demography on Growth) 

##A 3D  Scatter Plot.


```{r, echo=FALSE}
suppressMessages(library(plotly))
CorePop<-c(475,575,620,675)
Debt   <-c(250,400,2000,3500) 
GDP    <-c(200,250,750,1200)
Year   <-c(1990,2000,2010,2016) 

df<-data.frame(CorePop,Debt,GDP,Year,stringsAsFactors=FALSE) 

p<-plot_ly(df,x=~Debt,y=~GDP,z=~CorePop,
           marker=list(color=~CorePop,colorscale=
           c("violet","orange"),showscale=TRUE))%>%
add_markers()%>%
 layout( title='China - Changes in Core Population, Debt, GDP -     (1990-2006) - US$',
         
         scene=list(xaxis=list(title='Debt_bn'),
                   yaxis=list(title='GDP_bn'),
                   zaxis=list(title='CorePop_m')),
        
  annotations=list( 
   x=1.08,
   y=1.03,
   text= 'CorePop',
   showarrow=FALSE)) 
p
```





